% LaTeX template for (Academic) CV.
% The template consists only of this file.
% Document is to be structured as a normal article.
% Created in 2017 by Pedro Tiago Martins (ptmartins.info).
% Dedicated to the public domain.
% Source: https://github.com/ptsgmartins/cv-LaTeX-template

\documentclass[12pt]{article}
\usepackage{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{libertine} %font
\usepackage[margin=2cm]{geometry} %margins
\usepackage{fancyhdr} % header/footer
\usepackage{lastpage} %last page (for footer)
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{\thepage/\pageref{LastPage}}

\usepackage[usenames,dvipsnames,svgnames,x11names,table]{xcolor} % color
\newcommand{\cvcolor}{\color{DodgerBlue4}} %easier to change color consistently
\usepackage{doi} % easy input of doi numbers
\usepackage{enumitem} % customized lists (reset counters with the resume option)
\usepackage{titlesec} % customized section headers
\usepackage{titling} % customized title
\setlength\parindent{0em} 
\setlength{\parskip}{0.5em}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,            
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black},
    hyperfootnotes=true
}


%Section Header format
\titleformat{\section}
{\LARGE\scshape}{}{0em}{\cvcolor}[\titlerule]

\titleformat{\subsection}
{\large\scshape}{}{0em}{\cvcolor}

\titleformat{\subsubsection}
{\bfseries}{}{0em}{}

%Section header spacing
\titlespacing{\section}
{0em}{0em}{0em}

\titlespacing{\subsection}
{0em}{0.75em}{0em}

\titlespacing{\subsubsection}
{0em}{0em}{0em}

\usepackage{CJKutf8}

%Title
\renewcommand{\maketitle}{
\begin{center}
{\Huge\theauthor}\\
\vspace{0.5em}
{\Large \cvcolor{Curriculum Vitae}}\\
%{\itshape Graduate School of Economics and Management}\\
%{\itshape 41 Kawauchi, Aoba-ku, Sendai, Miyagi, Japan 980-8576}\\
%\vspace{0.25em}
{\color{Gray}(last update: \today)}
\end{center}
}

\begin{document}

\title{Curriculum Vitae} % doesn't actually show up anywhere
\author{Quang-Thanh Tran}

\maketitle


\section{Personal Info}
\textbf{Citizenship}: Vietnamese \\
\textbf{Email}: quangthanhtran.econ@gmail.com \\
\textbf{Tel}: (+84)-0911-055-240 \\
\textbf{ORCID}: \href{https://orcid.org/0000-0002-0308-1278}{0000-0002-0308-1278}\\
\textbf{Google Scholar}: \href{https://scholar.google.com/citations?user=rWZJIlwAAAAJ&hl=en}{user=rWZJIlwAAAAJ}\\
\textbf{Website}: \href{https://thanhqtran.github.io}{thanhqtran.github.io} \\
%\textbf{Japanese pronunciation}: \begin{CJK*}{UTF8}{min} クアンタイン　トラン　\end{CJK*}

%==========================================
%========= BIO ============================
%==========================================

\section{Research Fields}
Macroeconomics, Public economics, Demographic Economics, Economic Growth

%==========================================
%========= Employment ======================
%==========================================


\section{Employment}
\textbf{Research Fellow}, Development and Policies Research Center (DEPOCEN), Hanoi \hfill \emph{2025/07 -- current} \\
$\triangleright$ \textit{Conducting independent research on development economics, policy analysis, and macroeconomic modelling. Contributing to policy analysis and consulting works for NGOs and banks.} \\

\textbf{Visiting Fellow}, Research Center for Policy Design, Tohoku University \hfill \emph{2025/08 -- current} \\
$\triangleright$ \textit{Collaborating with faculty on research projects for sustainable development.} \\

\textbf{Research Fellow (DC2)}, Japan Society for the Promotion of Science, Japan \hfill \emph{2023/04 -- 2025/03} \\
$\triangleright$ \textit{Conducted doctoral research on demography and overlapping generations models.}

%==========================================
%========= EDUCATION ======================
%==========================================

\section{Education}

\textbf{PhD, Economics}\hfill\emph{March, 2025}\\
Tohoku University, Japan \\
%\textbf{Dissertation:} Three Essays on Fertility and Economic Growth \href{https://tohoku.repo.nii.ac.jp/record/2003894/files/250325-TRAN-221-1.pdf}{(PDF)}\\
\textbf{Academic Advisor:} Akiomi Kitagawa \\
\textbf{Referees:} Jiro Akita, So Kubota


\textbf{MA, Economics}\hfill\emph{September, 2021}\\
Tohoku University, Japan

\textbf{BA, International Economics}\hfill\emph{March, 2019}\\
Foreign Trade University (FTU), Vietnam

%==========================================
%========= RESEARCH ACHIEVEMENTS ==========
%==========================================
\clearpage
\section{Research}

\subsection{Publications}

\begin{enumerate}[label={[\arabic*]}]

\item \textbf{Tran, Q.T.} 2025. Fertility and Career Choices in an Overlapping Generations Model with Sandwich Caregivers. \textit{Economic Modelling}. 107262. \doi{10.1016/j.econmod.2025.107262}

\item \textbf{Tran, Q.T.} 2022. The Aging Tax on Potential Growth in Asia. \textit{Journal of Asian Economics}. 81, 101495. \doi{10.1016/j.asieco.2022.101495}
\end{enumerate}

\subsection{Work in Progress}

%\begin{enumerate}[resume*] %notice the resume* option; counter and format continue
\begin{enumerate}[label={[\arabic*]}]

\item Dual Caregiving, Declining Birth Rate, and Economic Sustainability, \textit{with} \href{https://researchmap.jp/read0118970?lang=en}{Akiomi Kitagawa}. \href{https://ideas.repec.org/p/dpc/wpaper/0325.html}{(DEPOCEN WP 193)} (submitted)

\item The Explosive Growth and Rapid Contraction of an Overlapping-Generations Economy. (R\&R). \href{https://depocenwp.org/upload/pubs/2025/199.pdf}{(DEPOCEN WP 199)}

\item Fertility and R\&D-based Growth: The Role of Higher Education \href{https://depocenwp.org/upload/pubs/2025/198.pdf}{(DEPOCEN WP 198)}

\item Demographic Change and Long-Run Inequality Trends: 30 Years of Evidence from Vietnam, \textit{with} \href{https://scholar.google.com/citations?user=uROWXaAAAAAJ&hl=vi}{Huy Le Vu}.

\item Old-Age Security in an Aging Economy: Revisited, \textit{with} \href{https://sites.google.com/view/vanquy93/}{Van-Quy Nguyen}.

\item Rational Addiction, Cigarette Consumption and Quitting Determinants, \textit{with} \href{https://scholar.google.com/citations?user=WcA9kdQAAAAJ&hl=en}{Tuong-Vy Phan} and \href{https://sites.google.com/depocen.org/anhnguyen/home?authuser=0}{Anh Ngoc Nguyen}.

\item What Drives Business Cycles in Vietnam? Evidence from an Estimated SOE DSGE Model.

\item The Roles of Fiscal and Monetary Policies in Vietnam: A New Keynesian Approach, \textit{with} \href{https://scholar.google.com/citations?user=zvwUmYkAAAAJ&hl=fr}{Cuong Le Van}.


\end{enumerate}

%==========================================
%========= GRANTS =========================
%==========================================

\section{Grants}

\textbf{JSPS Grants-in-Aid Research Fellowship for Young Scientists (DC2)}\hfill \emph{April 2023 -- March 2025}\\
Grant Number: 23KJ0135

\textbf{JST Pioneering Research Initiated by the Next Generation Program}\hfill \emph{October 2021 -- March 2023}\\
Grant Number: JPMJSP2114

\textbf{MEXT Honor Scholarship}\hfill \emph{April 2021 -- September 2021}

\textbf{Japanese Government's JASSO Scholarship}\hfill \emph{October 2019 -- March 2020}

\section{Awards}

\textbf{Best Paper Award}, Vietnamese Economist Annual Meeting 2025 \hfill \emph{December 2025}

\textbf{Best Paper Award}, The 18th Mirai Creation Prize, Tohoku University \hfill \emph{April 2023}

\textbf{Encouragement Scholarship for Outstanding Academic Results}, FTU \hfill \emph{August 2017}


%==========================================
%========= TEACHING =======================
%==========================================

\section{Teaching}

\subsection{Part-time Lecturer}
\begin{itemize}
	\item[ ] Optimization. National Economics University. Spring 2025.
\end{itemize}

\subsection{Bootcamp}
Graduate Student Organization's Intensive Bootcamps. URL: \href{https://github.com/thanhqtran/tohoku_bootcamp}{github.com/thanhqtran/tohoku\_bootcamp}.
\begin{itemize}
	\item[ ] Computational Macroeconomics (English, 20 hours in total) \hfill {\bf March 19 -- 26, 2024}
	\item[ ] Computational Macroeconomics  (English, 20 hours in total) \hfill {\bf September 2 -- 6, 2024}
	\item[ ] Special Topics in Macroeconomics (English, 20 hours in total) \hfill {\bf March 4 -- 8, 2024}
	\item[ ] Mathematics II (English, 30 hours in total)  \hfill {\bf August 28 -- September 15, 2023}
	\item[ ] Mathematics I  (English, 45 hours in total)  \hfill {\bf March 6 -- 24, 2023}
\end{itemize}

\subsection{Teaching Assistant}
\begin{itemize}
	\item[ ] Undergraduate Macroeconomics (Japanese). Professor: Akiomi Kitagawa \hfill {\bf Fall 2022}
 	\item[ ] Advanced Macroeconomics (Japanese). Professor: Michio Suzuki \hfill {\bf Fall 2022}
  	\item[ ] Formal Mathematics and Economic Modeling. Professor: Dai Zusai \hfill {\bf Spring 2022}
   	\item[ ] Computational Modeling and Simulation in Games. Professor: Dai Zusai \hfill {\bf Spring 2021}
    	\item[ ] Microeconomics I. Professor: Dai Zusai \hfill {\bf Spring 2021}
     	\item[ ] Microeconomics II. Professor: Dai Zusai \hfill {\bf Fall 2021}
\end{itemize}

%==========================================
%========= CONFERENCE PRESENTATIONS =======
%==========================================

\section{Presentations}

\begin{enumerate}[label={[\arabic*]}]
\item The 16th Vietnam Economist Annual Meeting (TUEBA, December 9-10, 2025)
\item MFE Seminar, National Economics University, February 2025
\item Joint workshop TU Research Center for Policy Design and Sophia Institute for Human Security, Tohoku University, March 2024
\item The 18th Macroeconomics Conference for Young Economists, Kyoto University, February 2024
\item Japanese Economic Association Fall Meeting, Kansai University, September 2023
\item The 14th Vietnam Economist Annual Meeting, University of Da Nang, July 2023
\item ISER Seminar Series, ISER, Osaka University, June 2023
\item The RCPD Research Seminar on Contemporary Economics, Tohoku University, September 2022
\item Japanese Economic Association Spring Meeting, Yokohama University, May 2022
\end{enumerate}

%\section{Service}
%
%\subsection{Reviewing}
%
%\subsubsection{Journals}
%
%\subsubsection{Conferences}
%
%\emph{ABC16} (2017)

\section{Programming Skills}

Python, R, Julia, MATLAB, STATA

\section{Languages}

\textbf{Vietnamese} (native), \textbf{English} (fluent), \textbf{Japanese} (advanced).

\section{Membership}

Japanese Economic Association, Asian and Australasian Society of Labour Economics, Vietnamese Economist Annual Meeting

\section{Other Activities and Training}

\textbf{Participant}, The IMF's 8th Macroeconomist Training Program. VENUE: JICA Tokyo (Tokyo International Center). DATE: January 9--10, 2020. \href{https://www.imf.org/en/countries/resrep/oap-home/2020/mtp-20200109}{in Press}.

\textbf{Participant}, IMFx's Monetary Policy Analysis and Forecasting. DATE of completion: October 11, 2025. \href{https://courses.edx.org/certificates/cba0e73cd51747e2ae0a105f8d9e9acc}{Certificate}.

\textbf{President}, Tohoku University Graduate Student Association. February, 2022 -- September, 2023

\textbf{President}, Vietnamese Student Association at Tohoku University. April, 2023 -- April, 2024

\section{\sc References}

\begin{center}
\begin{tabular}{p{7cm} p{7cm}}

% --- Row 1 ---
\parbox[t]{7cm}{
    {\bf \href{https://researchmap.jp/read0118970?lang=en}{Akiomi Kitagawa}} \\ 
    Professor of Macroeconomics \\
    at Tohoku University \\
    akiomi.kitagawa.a4@tohoku.ac.jp
}
&
\parbox[t]{7cm}{
    {\bf \href{https://researchmap.jp/read0055265?lang=en}{Jiro Akita}} \\ 
    Professor Emeritus of International Economics 
    at Tohoku University \\
    jiro.akita.b3@tohoku.ac.jp
}
\\[5 em]

% --- Row 2 ---
\parbox[t]{7cm}{
    {\bf \href{https://sites.google.com/depocen.org/anhnguyen/home?authuser=1}{Anh Ngoc Nguyen}} \\ 
    Chief Economist \\
    at DEPOCEN \\
    ngocanh@depocen.org
}

&
\parbox[t]{7cm}{
    {\bf \href{https://sites.google.com/view/yubaiecon/}{Yu Bai}} \\ 
    Assistant Professor of Economics \\
    at Tohoku University \\
    bai.yu.c2@tohoku.ac.jp
}
\\[5 em]

% --- Row 3 ---

\parbox[t]{7cm}{
    {\bf \href{https://researchmap.jp/read0006101?lang=en}{Cuong Le Van}} \\ 
    Professor Emeritus in PSE \\
    Research Director Emeritus at CNRS \\
    Cuong.Le-Van@univ-paris1.fr
}
&
\parbox[t]{7cm}{
    {\bf \href{https://en.em-normandie.com/professors-directory/thanh-tam-nguyen-huu}{Thi Kim Cuong PHAM}} \\ 
    Professor, Department of Economics \\
    at University of Paris Nanterre \\
    pham\_tkc@parisnanterre.fr
}
\\

\end{tabular}
\end{center}



\end{document}

% Local Variables:
% mode: latex
% End:
